Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-10 R0V0.tex
Item 10.

\begin{problem}\label{problem formulation}
	\begin{enumerate}[{P}$_1$.]\hfill
		\item For any forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$, find a feedback law $k^\ast$ such that, for every initial condition $x\in\mathbb{R}^n$, the issuing solution to  \eqref{eq:general system} in closed loop satisfies the inequality~\eqref{eq:global exponential uniform stabilizability}. Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, the $i$-th component $k^\ast$ depends on specific components of $x$ that are collected into a set $\mathscr{K}(i)$ of graph nodes;

		\item Given a graph $\mathscr{G}_c=(\mathscr{V}_c,\mathscr{E}_c)$ describing the communication network among the components of the controller, the set $\mathscr{K}(i)$ is composed of elements from $\mathscr{E}_c$.
	\end{enumerate}
\end{problem}

\mypara In other words, item P$_1$ of Problem~\ref{problem formulation} states that the controller is decomposed into smaller components. Each of these depends on the states  prescribed by the set $\mathscr{K}$. Item P$_2$ of Problem~\ref{problem formulation} states that this set may not necessarily correspond to the states which system~\eqref{eq:subsystem} depends on. This item addresses the case in which there exists a difference between the communication topology of the network represented by Equation~\eqref{eq:general system} and the communication topology of the distributed controller.

>>>>

\begin{problem}\label{problem formulation}
 For any forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$, find a feedback law $k^\ast$ such that, for every initial condition $x\in\mathbb{R}^n$, the issuing solution to  \eqref{eq:general system} in closed loop satisfies the inequality~\eqref{eq:global exponential uniform stabilizability}. Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, the $i$-th component $k^\ast$ depends on specific components of $x$ that are collected into a set $\mathscr{K}(i)$ of graph nodes;
\end{problem}

\mypara In other words, Problem~\ref{problem formulation} states that the controller is decomposed into smaller components. Each of these depends on the states  prescribed by the set $\mathscr{K}$. The definition of the set $\mathscr{K}$ is not restricted to the topology described by the graph $\mathscr{G}$. Given a graph $\mathscr{G}_c=(\mathscr{V}_c,\mathscr{E}_c)$ describing the communication network among different controllers, the set $\mathscr{K}$ can be defined as a subset of $\mathscr{V}_c$.
